Renal III

### 2017-05-29 renal3.rmd
updated quiz

@@

See Dan's autoregulation of kidney [GIFT](https://drive.google.com/drive/folders/0B0QeJC_rDeMIYjZMU2VfQVR2RU0)

@@

**Attach the image from the whiteboard**

@@

Pathophysiology of diabetic nephropathy: glycosylation of basement membrane => leaky => proteins flow out => thickening of arteriole (mainly efferent) [vasoconstriction] => decreases blood flow to peritubular capillaries => they start dying.

@@

-  Calcineurin inhibitors: tacrolimus and cyclosporin act and prevent IL-2 formation => no T cells
-  Antimetabolites: mycophenalate prevent B and T lymphocyte production
-  IL-2 R antag: basilixamab

@@

DDx: renal colic caused by kidney stones (aka nephrolithiasis), biliary colic (gall stones biliary tree), pyelonephritis, PKD => cyst rupture, (Female can be ovarian stuff), renal capsule stretched, malignancy

@@

Pathophysiology of HTN: build up of fluid => Down GFR => RAAS to increase BP. HTN is a risk factor for kidney stones

@@

Stones can lead to infection, hydronephrosis, decreased GFR, AKI => CKD, shitload of pain, rupture of ureter

>>>>

```{r setup, include=FALSE}
setwd("~/Documents/uni_work/4_sem_1/7111/lectures/15_renal_iii/readings")
```

@@

See Dan's autoregulation of kidney [**GIFT**](https://drive.google.com/drive/folders/0B0QeJC_rDeMIYjZMU2VfQVR2RU0)

# Quiz

-  Which of the following drugs must be used with particular caution in elderly patients with an existing low eGFR? 
    -  **Aspirin**
-  Which of the following indicates that kidney failure is chronic rather than acute? 
    -  Small kidneys
-  Pathophysiologic mechanism implicated in the development of diabetic nephropathy?
    -  Glomerulopathy due to glucose toxicity.
-  Epithelial cells on urine microscopy indicates contamination.
-  The commonest cause of death in severe chronic kidney disease is
    -   vascular disease
-  Greatest contributor to increase in CKD is diabetes mellitus NOT essential HTN/ageing population.

@@

![Was scribe](scibe-is-shit.jpg)

@@

Pathophysiology of diabetic nephropathy: glycosylation of basement membrane $\rightarrow$ leaky $\rightarrow$ proteins flow out $\rightarrow$ thickening of arteriole (mainly efferent) [vasoconstriction] $\rightarrow$ decreases blood flow to peritubular capillaries $\rightarrow$ they start dying.

@@

-  Calcineurin inhibitors: tacrolimus and cyclosporin act and prevent IL-2 formation $\rightarrow$ no T cells
-  Antimetabolites: mycophenalate prevent B and T lymphocyte production
-  IL-2 R antag: basilixamab

@@

DDx: renal colic caused by kidney stones (aka nephrolithiasis), biliary colic (gall stones biliary tree), pyelonephritis, PKD $\rightarrow$ cyst rupture, (Female can be ovarian stuff), renal capsule stretched, malignancy

@@

Pathophysiology of HTN: build up of fluid $\rightarrow$ Down GFR $\rightarrow$ RAAS to increase BP. HTN is a risk factor for kidney stones

@@

Stones can lead to infection, hydronephrosis, decreased GFR, AKI $\rightarrow$ CKD, shitload of pain, rupture of ureter
